---
title: "p8105_hw1_db3180"
author: "Divya Bisht"
date: 9/18/2018
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
# Problem 1
Creating a data frame:

```{r}
  problem1_df = tibble( 
    first_dist = runif(10, min = 0, max = 5),
    a_logical = first_dist > 2,
    b_char = c("blue", "green", "blue", "green", "blue", "green", "blue", "green", "blue", "green"),
    c_factor = factor(b_char)
)

```

The mean of the first_dist variable is `r mean(problem1_df$first_dist)'.

The mean of the a_logical variable is 'r mean(problem1_df$a_logical)'

The mean of the b_char variable is 'r mean(problem1_df$b_char)'

The mean of the c_factor variable is 'r mean(problem1_df$c_factor)'

It is only possible to take the mean of the first 'first_dist' and 'a_logical' vectors as they are numeric. The 'b_char' and 'c_factor' variables are characters and therefore cannot have a mean calculated. 

```{r}
as.numeric(problem1_df$a_logical)
as.numeric(problem1_df$b_char)
as.numeric(problem1_df$c_factor)
```


Converting variables
```{r}
as.numeric(a_logical, b_char, c_factor)
```
#Problem 2
Plotting

```{r}
set.seed(10)

plot_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
)

ggplot(plot_df, aes(x = x)) + geom_histogram()
```


