---
title: "p8105_hw1_db3180"
author: "Divya Bisht"
date: 9/18/2018
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
# Problem 1
Creating a data frame:

```{r}
  problem1_df = tibble( 
    first_dist = runif(10, min = 0, max = 5),
    a_logical = first_dist > 2,
    b_char = c("blue", "green", "blue", "green", "blue", "green", "blue", "green", "blue", "green"),
    c_factor = factor(b_char)
)

```

The mean of the first_dist variable is `r mean(problem1_df$first_dist)'.

The mean of the a_logical variable is 'r mean(problem1_df$a_logical)'

The mean of the b_char variable is 'r mean(problem1_df$b_char)'

The mean of the c_factor variable is 'r mean(problem1_df$c_factor)'

It is only possible to take the mean of the first 'first_dist' and 'a_logical' vectors as they are numeric. The 'b_char' and 'c_factor' variables are characters and therefore cannot have a mean calculated. 

Converting variables using as.numeric:
```{r}
as.numeric(problem1_df$a_logical)
as.numeric(problem1_df$b_char)
as.numeric(problem1_df$c_factor)
```
The logical vector and the factor vector give outputs, but the character vector outputs "NA".

Convert character variable from character to factor to numeric
Convert your factor variable from factor to character to numeric.
```{r}
convert_char = as.factor(problem1_df$b_char)
as.numeric(convert_char)

convert_factor = as.character(problem1_df$c_factor)
as.numeric(convert_factor)
```
Converting the character variable from character to factor to numeric was possible, but converting the factor to character and then to numeric was not possible. This is because you can't convert character variables into numeric variables. 

#Problem 2
Plotting

```{r}
set.seed(10)

plot_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
)

ggplot(plot_df, aes(x = x)) + geom_histogram()
```


